%-------------------------
% Resume in Latex
% Author : Sai Rohith Thota
% Reference : Sourabh Bajaj - https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*} {\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Sai Rohit Thota}} \\
  \href{https://github.com/Sairohithota}{github/Sairohithota}  & \href{mailto:sairohitthota@my.unt.edu}{sairohitthota@my.unt.edu}\\
   \href{https://www.linkedin.com/in/Sairohithota}{linkedin/Sairohithota} &  469-514-4706 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of North Texas}{Denton, Texas}
      {Master of Science in Data Science;  GPA: 3.66 }{Jan. 2018 -- Present}
    \resumeSubheading
      {Kakatiya Unversity}{Warangal, India}
      {Bachelor of Engineering in Computer Science;  GPA: 3.89}{Aug. 2013 -- Aug. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {HCL Technologies}{Hyderabad, India}
      {Data Analyst Intern }{Oct 2015 - Dec 2015}
      \resumeItemListStart
        \resumeItem{}
          {Performed Data Cleaning and Exploratory Data Analysis on HCL Customers Review Data}
         \resumeItem{}
          {Technologies: Unix, Tableau, Python}
          
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart  
  \resumeSubItem{Performance Analysis of Car Evaluation }
    \resumeItemListStart
      \resumeItem{}
      {This is a case study based on car evaluation dataset. Four different types of classification techniques (Decision Tree Classification, K nearest Neighbor Classification, Naïve Bayes Classification, Random Forest Classification) are applied on the dataset}
      \resumeItem{}
      { PCA and Gride Search are also performed on the Dataset. Predictive Model is built on the best classification technique}
      \resumeItem{}
      { Technologies: Python, AZURE Machine Learning Web services, Weka}
         \resumeItemListEnd
         
         

         
         
      \resumeSubItem{E-Medication}
      \resumeItemListStart
      \resumeItem{}
      {The objective of this application is that it allows the user to get instant guidance of their health condition (information about minor health related diseases) through an online system just on their fingertips}
      \resumeItem{}
      {Technologies: C\#,ASP.NET, MySql }
      \resumeItemListEnd
    
      \resumeSubItem{Interactive Data Visualization}
      \resumeItemListStart
      \resumeItem{}
      {Implemented Interactive Data Visualization Techniques on the English Premier League Data set. Created Data Visualizations Interactive Data Visualization where one can easily get know compelling facts about premier league teams}
       \resumeItem{}
      {Technologies: Tableau }
      \resumeItemListEnd
      \resumeSubItem{Text Mining and Information Retrieval System}
      \resumeItemListStart
      \resumeItem{}
      { Analyzed conference documents and implemented text mining techniques on the documents. Developed Fundamental components of an Information Retrieval System}
      \resumeItem{}
      { Technologies: Linux, SAS Enterprise Miner}
      
           \resumeItemListEnd
    \resumeSubItem{E-MARKETPLACE}
      \resumeItemListStart
      \resumeItem{}
      { Electronic marketplace where items are listed for sale or for purchase under various categories (which should will form a hierarchy). Coupon generation, Email Alerts, shipping method are implemented}
      \resumeItem{}
      {Technologies: WordPress, MySql}
      
           \resumeItemListEnd
      
      
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{: Python, R, C++, C, JAVA}
 
    \resumeSubItem{Database Technologies}{: MySql, NoSql}
    \resumeSubItem{Machine Learning}{: k-means, SVM, Random forest, Decision Tree, PCA, Grid Search}
    \resumeSubItem{Tools}{: WEKA, Rapid Miner, Tableau, Gretl, SAS, SPSS}
       \resumeSubItem{Operating System}{: Windows, Mac, Unix}
  \resumeSubHeadingListEnd
%-------------------------------------------

\end{document}
